June 2025 Lipid Interactome Monthly Invoice

### 2025-07-07 HourlyTracking/202506_GG-Hours.qmd
pushing small changes and hours log

---
title: "April 2025 Hours Report"
author: "Gaelen Guzman"
date: "2025 05 02"
output: 
  pdf_document:
    keep_tex: true
fontsize: 12pt
geometry: margin=1in
header-includes:
  - "\\usepackage{fancyhdr}"
  - "\\pagestyle{fancy}"
  - "\\fancyhead[L]{Gaelen Guzman}"
  - "\\fancyhead[C]{Hours Report}"
  - "\\fancyhead[R]{2025 06 02}"
  - "\\fancyfoot{}"
  - "\\renewcommand{\\headrulewidth}{0.4pt}"
  - "\\renewcommand{\\footrulewidth}{0pt}"
---

@@

Please find below the hours I logged for the month of May 2025, with descriptions of each day's activity. In total, I performed 8 hours of work at an hourly rate of $50 (USD), for a total bill of $400.

@@

# Read the Hours.csv file and handle unnamed columns
hours_data <- read_csv(here("HourlyTracking/hours.csv"), col_names = c("Date", "Hours", "Activity"), show_col_types = FALSE) |>
  mutate(Date = as.Date(as.character(Date), format = "%Y%m%d")) |>
  select(Date, Hours, Activity) |>
  filter(Date >= as.Date("2025-05-01") & Date < as.Date("2025-06-01")) %>%  # Filter for April 2025
  glimpse()

>>>>

---
title: "June 2025 Lipid Interactome Monthly Invoice"
author: "Gaelen Guzman"
date: "2025 07 01"
output: 
  pdf_document:
    keep_tex: true
fontsize: 12pt
geometry: margin=1in
header-includes:
  - "\\usepackage{fancyhdr}"
  - "\\pagestyle{fancy}"
  - "\\fancyhead[L]{Gaelen Guzman}"
  - "\\fancyhead[C]{Lipid Interactome Monthly Invoice}"
  - "\\fancyhead[R]{2025 07 01}"
  - "\\fancyfoot{}"
  - "\\renewcommand{\\headrulewidth}{0.4pt}"
  - "\\renewcommand{\\footrulewidth}{0pt}"
---

@@

Please find below the hours I logged for the month of June 2025, with descriptions of each day's activity. In total, I performed 9 hours of work at an hourly rate of $50 (USD), for a total bill of $450.

@@

# Read the Hours.csv file and handle unnamed columns
hours_data <- read_csv(here("HourlyTracking/hours.csv"), col_names = c("Date", "Hours", "Activity"), show_col_types = FALSE) |>
  mutate(Date = as.Date(as.character(Date), format = "%Y%m%d")) |>
  select(Date, Hours, Activity) |>
  filter(Date >= as.Date("2025-06-01") & Date < as.Date("2025-07-01")) %>%  # Filter for April 2025
  glimpse()
